si: code and prose exploring Spatial Interaction models

### 2022-06-13 README.qmd
Update name in library calls #20

```{r distance}
library(si)
library(dplyr)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(beta, d, m, n) {
  m * n * exp(-beta * d / 1000)
} 
# perform SIM
od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_production = origin_all,
  beta = 0.9
  )
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```

>>>>

```{r distance}
library(sim)
library(dplyr)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(beta, d, m, n) {
  m * n * exp(-beta * d / 1000)
} 
# perform SIM
od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_production = origin_all,
  beta = 0.9
  )
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```
